### 2012-09-28 doc/prelim/document/chapters/research_proposal/research_proposal.tex
working on challenge problem

\subsection{Parallel Performance and Numerical Accuracy Studies for MCSA
  Method}
\label{subsec:mcsa_studies}
A parallel MCSA implementation and our numerical test framework will
allow us to compare its performance to Krylov methods and allow us to
experiment with the way we combine it with the Neumann-Ulam solver. As
disucussed in \S~\ref{subsec:parallel_adjoint}, previous work with
MCSA used a correction generated by the Neumann-Ulam method with a
fairly large uncertainty near 14\%. We hypothesized that if we can
identify the amount of overlap in or Neumann-Ulam experiments required
to eliminate most transitions between adjacent domains owned by
different processors, then perhaps transport to adjacent domains can
be ignored. This will result in a biased estimator for the MCSA
correction that cannont be reproduced, however, these studies will aim
to determine if that bias and lack of reproducablity affects the
numerical results and reproducability of the MCSA method. Furthermore,
we will use the experimental framework to measure the convergence
rates for nonsymmetric systems and memory usage of the MCSA algorithm
and compare them to conventional Krylov methods using the same
framework.

\subsection{Parallel Performance and Numerical Accuracy Studies for FANM
  Method}
\label{subsec:fanm_studies}
Aside from resiliency motivations, the primary driver behind the FANM
method is reduced memory pressure due to the lack of additional
storage beyond that of the linear system in the MCSA method. The
nonlinear benchmark problems we have chosen will let us measure this
memory usage and compare it to conventional Newton-Krylov
methods. Furthermore, by varying the strength of the nonlinearities in
those problems (effectively by increasing the amount of convective
transport in the system), the benchmarks will become more difficult to
solve and require even more iterations to converge. This will give us
a means by which to vary the complexity of the system which we can
then compare to memory usage. Additionally, with the finite element
assembly framework we can choose functional discretizations of varying
accuracy, allowing us to vary the degrees of freedom in the system and
therefore also vary the memory required.

\section{Challenge Problem}
\label{sec:challenge_problem}

>>>>

\subsection{Parallel Performance and Numerical Accuracy Studies for MCSA
  Method}
\label{subsec:mcsa_studies}
A parallel MCSA implementation and our numerical test framework will
allow us to compare its performance to Krylov methods and allow us to
experiment with the way we combine it with the Neumann-Ulam solver. As
disucussed in \S~\ref{subsec:parallel_adjoint}, previous work with
MCSA used a correction generated by the Neumann-Ulam method with a
fairly large uncertainty near 14\%. We hypothesized that if we can
identify the amount of overlap in or Neumann-Ulam experiments required
to eliminate most transitions between adjacent domains owned by
different processors, then perhaps transport to adjacent domains can
be ignored. This will result in a biased estimator for the MCSA
correction that cannont be reproduced, however, these studies will aim
to determine if that bias and lack of reproducablity affects the
numerical results and reproducability of the MCSA method, yielding a
critical outcome for this work. Furthermore, we will use the
experimental framework to measure the convergence rates for
nonsymmetric systems and memory usage of the MCSA algorithm and
compare them to conventional Krylov methods using the same framework.

\subsection{Parallel Performance and Numerical Accuracy Studies for FANM
  Method}
\label{subsec:fanm_studies}
Aside from resiliency motivations, the primary driver behind the FANM
method is reduced memory pressure due to the lack of additional
storage beyond that of the linear system in the MCSA method. The
nonlinear benchmark problems we have chosen will let us measure this
memory usage and compare it to conventional Newton-Krylov
methods. Furthermore, by varying the strength of the nonlinearities in
those problems (effectively by increasing the amount of convective
transport in the system), the benchmarks will become more difficult to
solve and require even more iterations to converge. This will give us
a means by which to vary the complexity of the system which we can
then compare to memory usage. Additionally, with the finite element
assembly framework we can choose functional discretizations of varying
accuracy, allowing us to vary the degrees of freedom in the system and
therefore also vary the memory required for each problem.

\section{Challenge Problem}
\label{sec:challenge_problem}
Our numerical experiments will provide us with a set of metrics giving
best-performance solver parameters for problems of different types. As
an additional bonus, these experiments will let us further develop new
parallel implementations of the stochastic methods in order to improve
their performance and scalability. With these advancements in hand, we
look forward towards applying them to large-scale problems in reactor
physics.
